---
pagetitle: "CalCOFI Products"
editor_options: 
  chunk_output_type: console
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(
  echo = F, message = F, warning = F)
fontawesome::fa_html_dependency()
```

This website is dedicated to enabling and generating online products using data from the California Cooperative Oceanic Fisheries Investigations ([CalCOFI](https://CalCOFI.org)). By streamlining data ingestion into the database, summary extraction of data from the database using a public-facing API, and making helper functions available in an R library, we can easily produce interactive applications and online reports of value to scientific and management audiences.

```{r, }
librarian::shelf(
  bs4cards, bslib, dplyr, fontawesome, glue, googlesheets4, 
  htmltools, purrr, rstudio/webshot2)

# [datasheet | calcofi - Google Sheets](https://docs.google.com/spreadsheets/d/1ghM30pIdcsun7XWzLRKh4EilUplN60YdHayfiilPFwE/edit?pli=1#gid=600242061)
products_gs <- "https://docs.google.com/spreadsheets/d/1ghM30pIdcsun7XWzLRKh4EilUplN60YdHayfiilPFwE/edit"
products_tab <- "products"

gs4_deauth()

d_products <- read_sheet(products_gs, products_tab)

d_products <- d_products %>% 
  mutate(
    img = map2_chr(live_url, code, function(live_url, code){
      # d_products %>% filter(code == "capstone") %>% attach()
      img <- glue("./images/{code}.png")
      if (!file.exists(img))
        webshot(
          live_url, img,
          vwidth = 992,
          vheight = 744,
          delay = 5)
      img }))

# TODO: 
# - + date last updated
# - + Github icon: source_url
# - + Tags icon: categories

d_products %>% 
  arrange(title) %>% 
  cards(
    title = title,
    link = live_url,
    text = description_short,
    image = img,
    tags = paste("ALL;", categories),
    footer = categories,
    layout = "label-left",
    width = 4)
    # footer = map_chr(category, function(x){
    #   tagList(fa_i("tags"), x) %>% as.character() }))
```

Contacts: 

- Program: Erin Sattherwaite (esatterthwaite@ucsd.edu)
- Technical: Ben Best (ben@ecoquants.com)
