---
pagetitle: "CalCOFI Products"
editor_options: 
  chunk_output_type: console
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(
  echo = F, message = F, warning = F)
fontawesome::fa_html_dependency()
```

<!-- Google tag (gtag.js) -->
<script async src="https://www.googletagmanager.com/gtag/js?id=G-0HVK8TDMCF"></script>
<script>
  window.dataLayer = window.dataLayer || [];
  function gtag(){dataLayer.push(arguments);}
  gtag('js', new Date());

  gtag('config', 'G-0HVK8TDMCF');
</script>

This website is dedicated to enabling and generating online products using data from the California Cooperative Oceanic Fisheries Investigations ([CalCOFI](https://CalCOFI.org)). By streamlining data ingestion into the database, summary extraction of data from the database using a public-facing API, and making helper functions available in an R library, we can easily produce interactive applications and online reports of value to scientific and management audiences.

```{r}
# TODO: 
# - + date last updated
# - + Github icon: source_url
# - + Tags icon: categories

librarian::shelf(
  bs4cards, bslib, dplyr, fontawesome, glue, googlesheets4, 
  htmltools, purrr, rstudio/webshot2)

# [datasheet | calcofi - Google Sheets](https://docs.google.com/spreadsheets/d/1ghM30pIdcsun7XWzLRKh4EilUplN60YdHayfiilPFwE/edit?pli=1#gid=600242061)
products_gs <- "https://docs.google.com/spreadsheets/d/1ghM30pIdcsun7XWzLRKh4EilUplN60YdHayfiilPFwE/edit"
products_tab <- "products"

gs4_deauth()
d <- read_sheet(products_gs, products_tab)

d <- d %>% 
  mutate(
    img = map2_chr(live_url, key, function(live_url, key){
      # d_products %>% filter(key == "capstone") %>% attach()
      img <- glue("./images/{key}.png")
      if (!file.exists(img))
        webshot(live_url, img, delay = 3)
      img })) %>% 
  arrange(title) 

d %>% 
  mutate(
    text_source = map2_chr(description_short, source_url, function(x, y){
      glue("{x} <br>\n<a href='{y}'>\n  <img width=16 src='./images/icon_github.svg'> code</a>") } )) %>% 
  # pull(text_source) %>% .[[1]] %>% cat()
  cards(
    title  = title,
    link   = live_url,
    text   = text_source,
    image  = img,
    tags   = paste("ALL;", categories),
    footer = categories,
    layout = "label-left",
    width  = 4)
    # footer = map_chr(category, function(x){
    #   tagList(fa_i("tags"), x) %>% as.character() }))
```

Contacts: 

- Program: Erin Sattherwaite (esatterthwaite@ucsd.edu)
- Technical: Ben Best (ben@ecoquants.com)

<script>
$('.card-text').each(function() { 
  var x=$(this).text(); 
  $(this).html(x);
});
</script>
